---
title: "RStudio_Conf"
author: "Alexandre"
date: "January 17, 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## RStudio Conf
* 4 days in Orlando
    + 2-day training
        - Jackson: TidyVerse
        - Alexandre: Shiny
    + 2-day conference
        - Purrr, tidytext, Markdown, Github, RConnect

## Tidyverse

You can install tidyverse with

```{r, echo = TRUE, eval = FALSE}
install.packages("tidyverse")
```
```{r, echo = FALSE, include=FALSE}
library("tidyverse")
```

This will install the core tidyverse packages that you are likely to use in almost every analysis:

* ggplot2, for data visualisation.
* dplyr, for data manipulation.
* tidyr, for data tidying.
* readr, for data import.
* purrr, for functional programming.
* tibble, for tibbles, a modern re-imagining of data frame

## Shiny_Basic

```{r, echo = FALSE}
numericInput("rows", "How many cars?", 5)

renderTable({
  head(cars, input$rows)
})
```

## Shiny_Advanced

```{r, echo = FALSE}
shinyApp(
  
  ui = fluidPage(
    selectInput("region", "Region:", 
                choices = colnames(WorldPhones)),
    plotOutput("phonePlot")
  ),
  
  server = function(input, output) {
    output$phonePlot <- renderPlot({
      barplot(WorldPhones[,input$region]*1000, 
              ylab = "Number of Telephones", xlab = "Year")
    })
  },
  
  options = list(height = 500)
)
```


## Purr Package

* Set of functions for manipulating vectors
    + atomic vectors, lists, and data frames
    + similar to apply functions 

* Splits  mtcars dataset up by number of cylinders using the split() function
    + fits a linear model to each piece
    + summarises each model
    + then extracts the the \(R^2\):

```{r}
mtcars %>%
  split(.$cyl) %>%
  map(~lm(mpg ~ wt, data = .)) %>%
  map(summary) %>%
  map_dbl("r.squared")

```

## tidytext Package

* tidy text format as being a table with one-term-per-row
     + Sentiment analysis
     + word frequencies, relationship between words

```{r}
text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves - ",
          "and Immortality")
print(text)

text_df <- data_frame(line = 1:4, text = text)
library(tidytext)

text_df %>%
    unnest_tokens(word, text) %>%
    head(.,5)
```

## R Markdown

This is an R Markdown presentation. 

*   Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. 
    + For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
    + When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Github
* Clone the new GitHub repository to your computer via RStudio
    + *File > New Project > Version Control > Git*
    + Paste the URL of your new GitHub repository.
* Make local changes, save, commit
* Push your local changes online to GitHub - **Remember to pull and push**

* Clean up
    + **Local** It's just a regular directory on your computer.
    + **GitHub** Go to your repo's landing page on GitHub. Click on "Settings".
        - Scroll down, click on "delete repository"




